Lesson 5
========================================================

### Multivariate Data
Notes:

***

### Moira Perceived Audience Size Colored by Age
Notes:

***

### Third Qualitative Variable
Notes:

```{r Third Qualitative Variable}
ggplot(aes(x = gender, y = age),
       data = subset(facebook, !is.na(gender))) + geom_boxplot() + 
  stat_summary(fun.y = mean, geom = 'point', shape = 4)

ggplot(aes(x = age, y = friend_count),
       data = subset(facebook, !is.na(gender))) +
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)

library(dplyr)
fb.fcByAgeGen <- facebook %>%
                  filter(!is.na(gender)) %>%
                  group_by(age, gender) %>%
                  summarise(Me = mean(friend_count),
                            MD = median(friend_count),
                            n = n()) %>%
                  ungroup() %>%
                  arrange(age)
head(fb.fcByAgeGen)

ggplot(aes(x = age, y = MD), data = fb.fcByAgeGen) + 
  geom_line(aes(color = gender))
```

***

### Plotting Conditional Summaries
Notes:

```{r Plotting Conditional Summaries}

```

***

### Thinking in Ratios
Notes:

***

### Wide and Long Format
Notes:

***

### Reshaping Data
Notes:

```{r}
install.packages('reshape2')
library(reshape2)
fb.fcByAgeGen.wide <- dcast(fb.fcByAgeGen, 
                            age ~ gender,
                            value.var = 'MD')
head(fb.fcByAgeGen.wide)
```


***

### Ratio Plot
Notes:

```{r Ratio Plot}
ggplot(aes(x = age, y = female/male), data = fb.fcByAgeGen.wide) +
  geom_line() +
  geom_hline(yintercept = 1, alpha = 0.3, linetype = 2)

```

***

### Third Quantitative Variable
Notes:

```{r Third Quantitative Variable}
facebook$year_joined <- floor(2014 - (facebook$tenure/365))

```

***

### Cut a Variable
Notes:

```{r Cut a Variable}
summary(facebook$year_joined)
table(facebook$year_joined)

facebook$year_joined.bucket <- cut(facebook$year_joined, c(2004, 2009, 2011, 2012, 2014))
```

***

### Plotting it All Together
Notes:

```{r Plotting it All Together}
table(facebook$year_joined.bucket, useNA = 'ifany')

ggplot(aes(x = age, y = friend_count),
       data = subset(facebook, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = median)



```

***

### Plot the Grand Mean
Notes:

```{r Plot the Grand Mean}
ggplot(aes(x = age, y = friend_count),
       data = subset(facebook, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = mean, linetype = 2, color = 'black')

head(facebook)
```

***

### Friending Rate
Notes:

```{r Friending Rate}
with(subset(facebook, tenure >= 1), summary(friend_count/tenure))

```

***

### Friendships Initiated
Notes:

What is the median friend rate?

What is the maximum friend rate?

```{r Friendships Initiated}
ggplot(aes(x = tenure, y = friendships_initiated/tenure), data = facebook[facebook$tenure >= 1,]) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean)

ggplot(aes(x = 7 * round(tenure/7), y = friendships_initiated/tenure), data = facebook[facebook$tenure >= 1,]) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean)

ggplot(aes(x = tenure, y = friendships_initiated/tenure), data = facebook[facebook$tenure >= 1,]) +
  geom_line(aes(color = year_joined.bucket), stat = 'summary', fun.y = mean) +
  geom_smooth()

```

***

### Bias-Variance Tradeoff Revisited
Notes:

```{r Bias-Variance Tradeoff Revisited}

a <- ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(facebook, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

b <- ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(facebook, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

c <- ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(facebook, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

d <- ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(facebook, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

library(gridExtra)
grid.arrange(a, b, c, d, ncol = 1)
```

***

### Sean's NFL Fan Sentiment Study
Notes:

***

### Introducing the Yogurt Data Set
Notes:

***

### Histograms Revisited
Notes:

```{r Histograms Revisited}
yo <- read.csv('C:/Users/George varghese/Desktop/Analytics/Udacity/yogurt.csv')
str(yo)
yo$id <- factor(yo$id)

qplot(data = yo, x = yo$price, binwidth = 1, fill = I('#F79420')) +
  scale_x_continuous(breaks = seq(0, 72, 2))

ggplot(aes(x = price), data = yo) + geom_histogram()

```

***

### Number of Purchases
Notes:

```{r Number of Purchases}
unique(yo$price)
length(unique(yo$price))
table(yo$price)
length(unique(yo$id))

yo <- transform(yo, all.purchases = strawberry + blueberry + pina.colada + plain + mixed.berry)
head(yo)
```

***

### Prices over Time
Notes:

```{r Prices over Time}
qplot(data = yo, x = yo$all.purchases, binwidth = 1, fill = I('#F79420'))

ggplot(aes(x = time, y = price), data = yo) + geom_jitter(alpha = 1/4, shape = 21, fill = I('#F79420'))

```

***

### Sampling Observations
Notes:

***

### Looking at Samples of Households

```{r Looking at Sample of Households}
levels(yo$id)
set.seed(4231)
sample.ids <- sample(levels(yo$id), 16)

ggplot(aes(x = time, y = price), data = subset(yo, id %in% sample.ids)) +
  facet_wrap(~ id) +
  geom_line() +
  geom_point(aes(size = all.purchases), pch = 1)


```

***

### The Limits of Cross Sectional Data
Notes:

***

### Many Variables
Notes:

***

### Scatterplot Matrix
Notes:

```{r}
install.packages("GGally")
library(GGally)
theme_set(theme_minimal(20))
set.seed(1200)
fb_subset <- facebook[,c(2:15)]
ggpairs(fb_subset[sample.int(nrow(fb_subset), 1000), ])


```



***

### Even More Variables
Notes:

***

### Heat Maps
Notes:

```{r}
nci <- read.table("C:/Users/George varghese/Desktop/Analytics/Udacity/nci.tsv")
colnames(nci) <- c(1:64)
head(nci)
library(reshape2)
nci.long <- melt(as.matrix(nci[1:200, ]))
head(nci.long)

```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp, n = 100)
library(ggplot2)
ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```


***

### Analyzing Three of More Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

