Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}

```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
install.packages('ggplot2')
library(ggplot2)
```

***

#### What are some things that you notice about this histogram?
Response:

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}

```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes: 

***

### Moira's Outlier
Notes:
1. Eliminating the outliers, makes graphs look better and gives a better picture which is more accurate.

#### Which case do you think applies to Moira’s outlier?
Response: Bad data about an extreme case

OUtlier data can be good or bad as well. Its upto us to identify them and use them accordingly.

***


### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
library(ggplot2)
qplot(data = facebook, x = facebook$friend_count)

```

#### How is this plot similar to Moira's first plot?
Response: A lot of data in the left section of the graph between 0-500. And a very few occurences for points more than 1000. This cause the 1st bar to be really big as compared to others.

Its a long tailed data. Or skewed data

***

### Limiting the Axes
Notes:the parameter 'xlim' is the answer. It limits the x axes.

Another option is to add a layer using scale_x_continuous. The Y axis counterpart is scale_y_continuous

```{r Limiting the Axes}
qplot(data = facebook, x = facebook$friend_count, xlim = c(500, 1000))

qplot(data = facebook, x = facebook$friend_count) +
  scale_x_continuous(limits = c(0, 1000))

```

### Exploring with Bin Width
Notes: 

***

### Adjusting the Bin Width
Notes:
```{r}
qplot(data = facebook, x = friend_count, binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + scale_y_continuous(breaks = seq(0, 16000, 2000)) + facet_grid(gender ~.)

qplot(data = facebook, x = friend_count, binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + scale_y_continuous(breaks = seq(0, 16000, 2000)) + facet_wrap(~gender)

# Removing NA
qplot(data = facebook[!is.na(facebook$gender),], x = friend_count, binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + scale_y_continuous(breaks = seq(0, 16000, 2000)) + facet_wrap(~gender) 


```



### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}

qplot(data = na.omit(facebook), x = friend_count, binwidth = 25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) + scale_y_continuous(breaks = seq(0, 16000, 2000)) + facet_wrap(~gender) 

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
table(facebook$gender)
by(facebook$friend_count, facebook$gender, summary)
by()
```

#### Who on average has more friends: men or women?
Response: Women

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
Notes:

```{r Tenure}
qplot(x = tenure, data = facebook, binwidth = 30, color = I('black'), fill = I("#099DD9"))
qplot(x = tenure/365.5, data = facebook, binwidth = 0.25, color = I('black'), fill = I("#099DD9"),
      xlab = 'Number of years using Facebook', ylab = 'Number of users in sample') + 
  scale_x_continuous(breaks = seq(1, 7, 1), limits = c(0, 7))

```

### User Ages
Notes:

```{r User Ages}
qplot(data = facebook, x = age, binwidth = 1, color = I("black")) + 
  scale_x_continuous(breaks = seq(0, 100, 10), limits = c(0, 100))

```


### Lada's Money Bag Meme
Notes: She observed 1 particular meme which kept occuring on particular dates spread over months. The meme was:
"This month has 5 Fridays, a phenomenon seen online once in 800 years etc......"
In this she tried to analyse the spread of memes. 

***

### Transforming Data
Notes:

```{r}
qplot(data = facebook, x = friend_count)

summary(facebook$friend_count)

summary(log10(facebook$friend_count + 1))

summary(sqrt(facebook$friend_count))


#grid layout

p1 <- qplot(x = friend_count, data = facebook, colour = I('black'))
p2 <- qplot(x = log10(friend_count + 1), data = facebook, colour = I('black'))
p3 <- qplot(x = sqrt(friend_count), data = facebook, colour = I('black'))

# arrange plots in grid
grid.arrange(p1, p2, p3, ncol=1)

```

***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}
#grid layout using scales - Alternate Solution

p1 <- ggplot(aes(x = friend_count), data = facebook) + geom_histogram()
p2 <- p1 + scale_x_log10()
p3 <- p1 + scale_x_sqrt()

grid.arrange(p1, p2, p3, ncol=1)
```

***


### Frequency Polygons
Notes: Helps to compare distributions

```{r Frequency Polygons}
qplot(data = facebook[!is.na(facebook$gender),], x = friend_count, binwidth = 10, 
      geom = "freqpoly", color = gender) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))


qplot(data = facebook[!is.na(facebook$gender),], x = friend_count, y = ..count../sum(..count..),
      xlab = 'Friend Count', ylab = 'Percentage of users with that friend count',
      binwidth = 10, geom = "freqpoly", color = gender) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50))


```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
library(ggplot2)

qplot(data = facebook[!is.na(facebook$gender),], x = www_likes, geom = "freqpoly", color = gender) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 1000, 50)) +
  scale_x_log10()

sum(facebook$www_likes[facebook$gender == 'male'], na.rm = TRUE)

by(facebook$www_likes, facebook$gender, sum)

```


***

### Box Plots
Notes:

```{r Box Plots}
qplot(x = gender, y = friend_count, 
      geom = 'boxplot', data = facebook[!is.na(facebook$gender),], ylim = c(0, 500)) + 
  scale_y_continuous(limits = c(0, 1000))

qplot(x = gender, y = friend_count, 
      geom = 'boxplot', data = facebook[!is.na(facebook$gender),]) + 
  coord_cartesian(ylim = c(0,250))

by(facebook$friend_count, facebook$gender, sum)

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
```{r}
by(facebook$friendships_initiated, facebook$gender, summary)
qplot(x = gender, y = friendships_initiated, geom = 'boxplot', 
      data = facebook[!is.na(facebook$gender),]) + 
  coord_cartesian(ylim = c(0, 150))

```



***

### Getting Logical
Notes:

```{r Getting Logical}
facebook$mobile_check_in <- NA
facebook$mobile_check_in <- ifelse(facebook$mobile_likes > 0, 1, 0)
facebook$mobile_check_in <- factor(facebook$mobile_check_in)
summary(facebook$mobile_check_in)

```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!