Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes: People underestimated their audience size which could be seen through the scatter plot.

***

### Scatterplots
Notes:

```{r Scatterplots}

facebook <- read.csv("C:/Users/George varghese/Desktop/Analytics/Udacity/EDA_Course_Materials/lesson3/pseudo_facebook.tsv",
           header = TRUE, sep = "\t")

qplot(x = age, y = friend_count, data = facebook)


```


### ggplot Syntax
Notes:

```{r ggplot Syntax}

ggplot(aes(x = age, y = friend_count), data = facebook) + 
  xlim(13, 90) + 
  geom_jitter(alpha = 1/20)

ggplot(aes(x = age, y = friend_count), data = facebook) + 
  xlim(13, 90) + 
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) + 
  coord_trans(y = "sqrt")

ggplot(aes(x = age, y = friendships_initiated), data = facebook) +
  geom_point(alpha = 1/10, position = position_jitter(h = 0)) +
  coord_trans(y = "sqrt")


```


### Conditional Means
Notes:

```{r Conditional Means}
install.packages("dplyr")
library(dplyr)
age_groups <- group_by(facebook, age)
head(age_groups)

fb.fc_by_age <- summarise(age_groups, 
                          fcm = mean(friend_count),
                          fcmed = median(friend_count),
                          n = n())

fb.fc_by_age <- arrange(fb.fc_by_age, age)

head(fb.fc_by_age)

#Alternate
facebook %>%
  group_by(age) %>%
  summarise(fcm = mean(friend_count),
            fcmed = median(friend_count),
            n = n()) %>%
  arrange(age)

```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x = age, y = fcm), data = fb.fc_by_age) +
  geom_line()

ggplot(aes(x = age, y = fcm), data = fb.fc_by_age) +
  geom_point() + geom_path()


```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
p1 <- ggplot(aes(x = age, y = friend_count), data = facebook) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0), color = "orange") + 
  geom_line(stat = "summary", fun.y = mean) + 
  geom_line(stat = "summary", fun.y = quantile, fun.args=list(probs=0.1), linetype = 2, color = 'blue') + 
  geom_line(stat = "summary", fun.y = quantile, fun.args=list(probs=0.9), linetype = 2, color = 'blue') +
  geom_line(stat = "summary", fun.y = quantile, fun.args=list(probs=0.5), color = 'blue') + 
  coord_cartesian(xlim = c(0,30), ylim = c(0, 1000))

p2 <- ggplot(aes(x = age, y = friend_count), data = facebook) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0), color = "orange") + 
  geom_line(stat = "summary", fun.y = mean) + 
  geom_line(stat = "summary", fun.y = quantile, fun.args=list(probs=0.1), linetype = 2, color = 'blue') + 
  geom_line(stat = "summary", fun.y = quantile, fun.args=list(probs=0.9), linetype = 2, color = 'blue') +
  geom_line(stat = "summary", fun.y = quantile, fun.args=list(probs=0.5), color = 'blue') + 
  coord_cartesian(xlim = c(30, 60), ylim = c(0, 1000))

p3 <- ggplot(aes(x = age, y = friend_count), data = facebook) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0), color = "orange") + 
  geom_line(stat = "summary", fun.y = mean) + 
  geom_line(stat = "summary", fun.y = quantile, fun.args=list(probs=0.1), linetype = 2, color = 'blue') + 
  geom_line(stat = "summary", fun.y = quantile, fun.args=list(probs=0.9), linetype = 2, color = 'blue') +
  geom_line(stat = "summary", fun.y = quantile, fun.args=list(probs=0.5), color = 'blue') + 
  coord_cartesian(xlim = c(60, 75), ylim = c(0, 1000))

library(gridExtra)
grid.arrange(p1, p2, p3, ncol=1)


# no grids.. all age groups
ggplot(aes(x = age, y = friend_count), data = facebook) +
  geom_point(alpha = 1/20, position = position_jitter(h = 0), color = "orange") + 
  geom_line(stat = "summary", fun.y = mean) + 
  geom_line(stat = "summary", fun.y = quantile, fun.args=list(probs=0.1), linetype = 2, color = 'blue') + 
  geom_line(stat = "summary", fun.y = quantile, fun.args=list(probs=0.9), linetype = 2, color = 'blue') +
  geom_line(stat = "summary", fun.y = quantile, fun.args=list(probs=0.5), color = 'blue') + 
  coord_cartesian(xlim = c(13, 75), ylim = c(0, 1000))
```

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
?cor.test
cor.test(facebook$age, facebook$friend_count, method = "kendall")

with(facebook, cor.test(age, friend_count, method = "pearson"))

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(facebook, age <= 70), cor.test(age, friend_count))
```

***

### Correlation Methods
Notes: Spearman, Pearson and Kendall

***

## Create Scatterplots
Notes:

```{r}
ggplot(data = facebook, aes(x = www_likes_received, y = likes_received)) +
  geom_point() + 
  xlim(0, quantile(facebook$www_likes_received, 0.95)) + 
  ylim(0, quantile(facebook$likes_received, 0.95)) +
  geom_smooth(method = 'lm', color = 'red')
  
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
cor.test(facebook$www_likes_received, facebook$likes_received, method = "pearson")

```

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3', dependencies = TRUE)
library(alr3)
data(Mitchell)

```

Create your plot!

```{r Temp vs Month}
ggplot(data = Mitchell, aes(x = Month, y = Temp)) +
  geom_point()

qplot(data = Mitchell, Month, Temp)

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

```{r}
ggplot(data = Mitchell, aes(x = Month, y = Temp)) +
  geom_point() +
  scale_x_discrete(breaks = seq(0, 203, 12))


```


***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
ggplot(aes(x = age, y = fcm), data = fb.fc_by_age) + 
  geom_line()

facebook$age_withMonths <- facebook$age + (12 - facebook$dob_month)/12


```

***

### Age with Months Means

```{r Age with Months Means}
fb.fc_by_ageMonths <- facebook %>%
  group_by(age_withMonths) %>% summarise(fcm = mean(friend_count),
                                         fcmed = median(friend_count),
                                         n = n()) %>%
  arrange(age_withMonths)


#Alternate
age_groups <- group_by(facebook, age)
head(age_groups)

fb.fc_by_age <- summarise(age_groups, 
                          fcm = mean(friend_count),
                          fcmed = median(friend_count),
                          n = n())

fb.fc_by_age <- arrange(fb.fc_by_age, age)

```

Programming Assignment
```{r Programming Assignment}

ggplot(aes(x = age_withMonths, y = fcm), data = fb.fc_by_ageMonths[fb.fc_by_ageMonths$age_withMonths <= 71,]) +
  geom_point()
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}
p1 <- ggplot(aes(x = age, y = fcm), data = subset(fb.fc_by_age, age < 71)) + 
  geom_line() + geom_smooth()

p2 <- ggplot(aes(x = age_withMonths, y = fcm), data = fb.fc_by_ageMonths[fb.fc_by_ageMonths$age_withMonths <= 71,]) +
  geom_line() + geom_smooth()

p3 <- ggplot(aes(x = round(age/5)*5, y = friend_count), data = subset(facebook, age < 71)) + 
  geom_line(stat = "summary", fun.y = mean)

library(gridExtra)
grid.arrange(p1, p2, p3, ncol = 1)

```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

